Flowchart of Current Algorithm

### 2009-02-03 docs/flowchart/flowchart.tex
cleaning up the Initialization Step to 'look' more like the code

Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ an 
initial base state, and an initial guess for the velocity, $\Ub^{\initp}.$
Use the equation of state to determine $(\rho h)^{\initp}$.  Set
$w_0^1 = 0$ as an initial approximation.  Compute $\beta_0^{\initp}$ as a function of 
the initial data.  Then, project $\Ub^{\initp}$ using $\beta_0^{\initp}$ and 
$S = \rho\Hext$, giving $\Ub^{0,1}$.  The next part of the initialization process 
proceeds as follows.

@@

  \item Estimate $\Delta t^\nu$ using $\Ub^{0,\nu}$ and $w_0^\nu.$

@@

  \item Compute $w_0^{\nu+1}$ as in step 1c using $\overline{S^{0,\nu}}$ and $\psi^{\nmh} = 0$.

  \item Project $\Ub^{0,\nu}$ using $\beta_0^{\initp}$ and 
        $(S^{0,\nu} - \overline{S^{0,\nu}})$ as the source term.  
        This yields $\Ub^{0,\nu+1}.$

@@

  Define $S^0 = S^{0,N_{\rm iters}^S}$, $w_0^{-\myhalf} = w_0^{N_{\rm iters}^S+1}$, 
$\dt^0 = \Delta t^{N_{\rm iters}^S},$ and $\Ub^0 = \Ub^{0,N_{\rm iters}^S+1}.$

@@

Next, we need to construct an approximation to the time-centered perturbational pressure,
$\pi,$  and an approximation to the divergence constraint at the end of the
first time step.  As initial approximations, set $S^{1,0} = S^0$,
$\etarho^{-\myhalf} = 0$, $\psi^{-\myhalf} = 0$, and $\pi^{-\myhalf} = 0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}

\item {\bf Do} {$\nu = 0,...,N_{\rm iters}^{\pi}-1$.}

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\myhalf,\star} = (S^0 + S^{1,\nu})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S^{1}}\right) - \left(S^{0}-\overline{S^{0}}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\myhalf}$ (step 8), $\psi^{\myhalf}$ (step 8), 
      $S^{1,\nu+1}$ (step 10), and $\pi^{\myhalf}$ (step 11), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}

>>>>

Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ an 
initial base state, and an initial guess for the velocity, $\Ub^{\initp}.$
Use the equation of state to determine $(\rho h)^{\initp}$.  Set
$w_0^0 = 0$ as an initial approximation.  Compute $\beta_0^{\initp}$ as a function of 
the initial data.  Then, project $\Ub^{\initp}$ using $\beta_0^{\initp}$ and 
$S = \rho\Hext$, giving $\Ub^{0,0}$.  The next part of the initialization process 
proceeds as follows.

@@

  \item Estimate $\Delta t^\nu$ using $\Ub^{0,\nu-1}$ and $w_0^{\nu-1}.$

@@

  \item Compute $w_0^{\nu}$ as in step 1c using $\overline{S^{0,\nu}}$ and $\psi=0$.

  \item Project $\Ub^{0,\nu-1}$ using $\beta_0^{\initp}$ and 
        $(S^{0,\nu} - \overline{S^{0,\nu}})$ as the source term.  
        This yields $\Ub^{0,\nu}.$

@@

  Define $S^0 = S^{0,N_{\rm iters}^S}$, $w_0^{-\myhalf} = w_0^{N_{\rm iters}^S}$, 
$\dt^0 = \Delta t^{N_{\rm iters}^S},$ and $\Ub^0 = \Ub^{0,N_{\rm iters}^S}.$

@@

Next, we need to construct an approximation to the time-centered perturbational pressure,
$\pi,$  and an approximation to the divergence constraint at the end of the
first time step.  As initial approximations, set $\etarho^{-\myhalf}=0$, $\psi^{-\myhalf}=0$,
$S^{1,0}=S^0$, and $\pi^{-\myhalf}=0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}

\item {\bf Do} {$\nu = 1,...,N_{\rm iters}^{\pi}$.}

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\myhalf,\star} = (S^0 + S^{1,\nu-1})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S^{1}}\right) - \left(S^{0}-\overline{S^{0}}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\myhalf}$ (step 8), $\psi^{\myhalf}$ (step 8), 
      $S^{1,\nu}$ (step 10), and $\pi^{\myhalf}$ (step 11), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}
